Working title: Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-12-16 write_up/reviewer_response.tex

\documentclass{article}

\usepackage[a4paper, margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{lscape}
\usepackage{longtable}
\usepackage{hhline}
\usepackage{booktabs}

\begin{document}

\large

Address here: cover letter on other computer. \\
\\
Dear xyz, \\
RE: Ms. No. ECOMOD-19-631 \\
\\
Thank you for your email of 5 December 2019 with a favourable review of our
manuscript submission. We have reviewed all the comments made by the editor and
the two reviewers and adjusted the manuscript accordingly. We thank the
reviewers for a constructive review which undoubtedly improves the manuscript
and we found little reason to disagree with their comments. A summary of our
changes are presented overleaf. \\

We look forward to hearing back positively on these changes, and publication of
the manuscript in Ecological Modelling. \\
\\
Kind Regards,\\
\\
Paul J. Dolder, Cóilín Minto, Jean-Marc Guarini \& Jan Jaap Poos

\newpage

\begin{landscape}

\underline{Editor's comments} \\
\\
\textit{
After considering the comments of the two reviewers, which are provided below,
I think your manuscript should be acceptable for publication after satisfactory
revision.  Please address the reviewers' comments when revising your
manuscript.  Thank you again for submitting your manuscript to Ecological
Modelling.
} \\

Thank you for your comments, we have provided a detailed response to each of
the points made by the reviewers; we hope this satisfies your requirements and
look forward to seeing the manuscript published. \\

\underline{Reviewer 1 comments} \\

\textit{This paper introduces a simulation framework for assessing the effects
	of different spatial and temporal observation scales on management of
	mixed fisheries. An application of the framework is presented, and the
	findings from the example application provided insights into the
	importance of data resolution on design and effectiveness of closed
	areas. The model code is included as an R package so that other
	researchers will be able to implement it readily to address a wide
	variety of management questions. The question of appropriate scales is
	an important one, and I think this will be a valuable tool for
	researchers and managers. I recommend that it be published after minor
	revisions.} \\

Thank etc..

\large
	\begin{center}
	\begin{longtable}{p{12cm} | p{12cm}}
%	\caption{Highly resolved spatiotemporal simulations for exploring mixed
%	fishery dynamics}
		\toprule
		Comment & Response \\
		\\
		\hline
		\\
		\textbf{Abstract} & \\
\\
I think it would be helpful to mention the name of the R package (MixFishSim)
that accompanies this paper somewhere in the abstract. People will search for
the package name, it would be nice if the term was included in the abstract so
the paper will show up in the search too. & Thank you, we agree and have
included in the first sentence of the abstract. \\
\\
"true underlying populations" - somehow make sure readers know this is
referring to simulated populations. & We have changed to "true (simulated)
underlying populations" \\
\\
Could add something like "bycatch avoidance", or something like that, somewhere
in key words or abstract; people searching for that term would be glad to find
this paper, I would think! & \\
\\
I think the abstract could be streamlined a bit. You seem to have 2 major
objectives with this paper: 1) introducing and describing the simulation
framework that could answer a number of important management questions, and 2)
demonstrating its usefulness with an example application. One full paragraph
for each should be adequate, with a conclusion that states the usefulness of
the framework for answering a number of fisheries management questions.  & \\
\\
		\hline
		\textbf{Introduction} &  \\
\\
Nice introduction to the need for the simulation framework & Thank you, we have
kept this text unchanged. \\
\\
Line 62: "Do different sources of sampling-derived fisheries data reflect"… &
Thanks, corrected. \\
\\
		\hline
		\textbf{Methods} &  \\
\\
Why was the Matern covariance structure chosen? I am just curious about this;
does it reflect the spatial autocorrelation of animal distributions better than
a Gaussian or other type of covariance structure? & \\
\\
It would be helpful to have explanation of thermal tolerance earlier than line
155 & \\
\\
The paragraph starting at line 179 would be helpful to have at the beginning of
the section & \\
\\
Line 187, make tenses consistent (e.g. determined vs. determines) - also this
sentence is a little awkward to read. & \\
\\
		\hline
		\textbf{Results} &  \\
\\
Line 376: What does "Visualized using Gerritsen (2014)" mean? & \\
\\
Line 397: Are these the same figures in Table 7? If so, just refer to the table
and summarize & \\
\\
Line 400: move \% sign & This has been corrected. [Note, may be redundant if
change text] \\
\\
Line 406: "(in red)" - leave reference to color for figure legend & Removed
reference to color. \\
\\
Line 410: "Again" doesn't need to be there, same in line 413 & Agree, it has
been removed. \\
\\
Line 416: This section is a little confusing and needs to be refined/streamlined. & \\
\\
Line 418: This paragraph should be in methods. But you did it for all
populations, right? Not just population 3? & \\
\\
		\hline
		\textbf{Discussion / Conclusion} &  \\
\\
The discussion and conclusion overlap a bit; I felt I was reading similar
things over again; perhaps these can be streamlined? & \\
\\
Line 560: change "reduced" to "reduce" & Thank you, corrected. \\
\\
Line 663: change "hypothesis" to "hypotheses" & Done. \\
\\
		\hline
		\textbf{Figures} &  \\
\\
Figure 1: nicely summarizes the model. It took me a little bit to figure out
that "Rec" referred to recruitment - even though it was in the legend (I missed
it when I read it the first time)… is it possible to choose an abbreviation
that makes it more obvious, maybe something like "Recruit" or  even "Recr"? It
also occurs to me that there is an opportunity to introduce the terminology
from your R package here to make it very clear to the people using your code
how the functions work together… this is only an idea though… or maybe a
similar figure could be included with the vignette. & \\
\\
Figure 5: Do the colors indicate the dominant population in each cell? It is
hard to imagine that one would assume only the presence of specific population
in the cell? Or do I have the wrong idea about what the plot is showing? & \\
\\
Figure 9: So the top two panels show spatial distribution for population 3?
That needs to be added to the legend. Also there should be a red box on the top
plot too. & \\
\\
Figure 10: I really like this plot! Very effective. & \\
		\bottomrule
	\end{longtable}

\end{center}

\underline{Reviewer 2 comments} \\

\textit{The paper Dolder et al. presents a new highly resolved spatiotemporal
	model that simulates populations of species and fishery dynamics to
	assess if data from commercial catches and fixed-site sampling surveys
	on different spatiotemporal scales represent the real distribution of
	the populations, and if these data are effective to base  management
	programs. Moreover, they presents other applications of the model.} \\

\textit{This is a very interesting paper, and the model provides several
	applications for management programs. I have only few greater questions
	and some small issues, most of them about the presentation of the
	information.}  \\

Thank etc..

\begin{center}

\large

	\begin{longtable}{p{12cm} | p{12cm}}
%	\caption{Highly resolved spatiotemporal simulations for exploring mixed
%	fishery dynamics}
		\toprule
		Comment & Response \\
		\\
		\hline
		\\
	\textbf{General comments} &  \\
\\
		 How many species does the model simulate? The authors refer to
		 the issue of catching unwanted species (vulnerable or low
		 quota species) when available quota species is caught, and it
		 suggested me that populations of different species is modeled
		 at the same time. However, they  did not describe how many
		 species could be simulated in each simulation, only that four
		 populations were simulated. Does the populations simulated in
		 different simulations, or all of them are simulated
		 simultaneously? The results indicate that the four populations
		 were simulated in the same simulation. Please, clarify this in
		 the MM.  &  \\
\\
There are too many figures and they should be better edited. Why the name of
the row and columns are inside the graphics? The axes scales and the axes title
should be greater. I would also send the figure 2, 3 and 9 as supplementary
data.  & \\
\\
The legends of the supplementary figures should be more informative. In the
Figure S2, what the light gray spots are? Habitat preference? Are the squares
the spawning areas? In the figure S3, are each square a week?  & \\
\\
I am not native English, but the language seems good for me. However, I missed
several commas along the text that make the sentences too long and hard to
understand. I suggest a revision of this.  & \\

		\hline

	\textbf{Small issues} &  \\
\\
Line 14 - 18: This phrase is too long and hard to understand. Please, rephrase
this in shorter sentences to clarify this idea. & \\
\\
Lines 20 - 43: These two paragraphs seem redundant.  & \\
\\
Line 68 - 72: The authors mentioned that the MixFishSim could be used to infer
if fisheries data are the real community structure. I suggest adding one or two
phrases to explain how the model could help in this. & \\
\\
Line 90. The authors presented the time-step of each module, except the
Recruitment dynamics. The recruitment dynamics probably follow the population
dynamic, but it would be interesting present this explicitly. & \\
\\
Line 282: How these population parameters were selected? Randomly? Using real
data? Or the authors only created them? & \\
\\
Line 426: What does adapted means in this context? Exploring new opened areas?
& \\
\\
Line 613: Do not use parenthesis inside of other parenthesis. & We have changed
to ", e.g." from "( e.g." to eliminate one set of parenthesis. \\
\\
Table 2 and table 3 are not cited in the text Citation of the supplementary
figures are out of order & \\
\\
Figure 3: Individual years ARE the light grey lines    & Thanks! Corrected. \\
\\
Figure 4. What do the purple spots represent? Describe these spots in the
capture Figure 7. Add what " res"  means in the caption.  & \\
\\
Figure 8. What F means? & \\
\\
		\bottomrule
	\end{longtable}

\end{center}

\end{landscape}

\end{document}

### 2019-12-16 write_up/mixfishsim_ecolmod_revisions.tex
Responding to reviewer comments

@@

%% Group authors per affiliation:
\author[1,2]{Paul J. Dolder\corref{c}}
\cortext[c]{Corresponding author}
\ead{paul.dolder@research.gmit.ie}

@@

%%
To understand how data resolution impacts inference on mixed fisheries
interactions we developed a highly resolved spatiotemporal discrete-event
simulation model incorporating: i) delay-difference population dynamics, ii)
population movement using Gaussian Random Fields to simulate patchy,
heterogeneously distributed populations, and iii) fishery dynamics for multiple
fleet characteristics based on population targeting under an explore-exploit
strategy. This is implemented via a mix of correlated random walk movement (for
exploration) and learned behaviour (for exploitation) phases of the fisheries. \\ 
%%
Fifty years of sub-daily fishing activity was simulated and used to draw
inference on the underlying community structures. We compared inferences based
on: commercial catch, a simulated fixed-site sampling survey design and the
true underlying populations. We i) establish the potential limitations of
fishery-dependent data in providing a robust picture of spatiotemporal
distributions; and then ii) simulated an area closure based on areas defined
from the different data sources at a range of temporal and spatial resolutions.\\
%%
Our framework allows users to explore the assumptions in modelling
observational data and evaluate the underlying dynamics of such approaches at a
fine spatial and temporal scale. In application to a mixed fishery exploiting
four different populations we found different spatial patterns were evident and
that the effectiveness of the spatial closure reduced when data were aggregated
across larger spatial areas. However, aggregation across time periods has less
of a negative impact on the closure success and while not as effective as when
based on on the true population, closures based on high catch rates observed in
commercial data could still reduce fishing on a protected species. \\

@@

\begin{enumerate}
	\item Do different source of sampling-derived fisheries data
		reflects the underlying community structure? 	
	\item How does data aggregation and data source impact on the success
		of spatial fisheries management measures?
\end{enumerate}

@@

Different perceptions of the proportion of each stock in an area are seen when
we aggregate the data over a smaller geographical region at different
timescales, with weekly (top), monthly (middle) and yearly (bottom) catch
compositions from across an aggregated 20 x 20 area (Figure \ref{fig:2}). In
the true population, the monthly aggregation captures the major patterns of
composition seen in the weekly data with the percentage of different
populations in the catch having similar mean and standard deviations.  In the
weekly data population 1 = 9.36\% (SD = 3.99), population 2 = 83.2\% (5.60),
population 3 = 3.57\% (1.23), population 4 = 3.91\% (1.59); in the monthly data
population 1 = 9.23\% (3.87), population 2\% = 83.3 (5.52), population 3 =
3.62\% (1.15), population 4 = \%3.86 (1.52). While means were similar some of
the variation was lost when aggregated to an annual level; population 1 =
9.90\% (0.173), population 2 = 82.2\% (0.308), population 3 = 3.82\% (0.119),
population 4 = 4.03\% (0.0502).\\

The commercial data on a weekly basis shows some of the same patterns as the
true population, though the population 1 (in red) is less well represented and
some weeks are missing catches from the area. Here, weekly and monthly
compositions were nearly identical, with monthly composition of population 1 =
0.0472\% (0.0139), population 2 = 94.4\% (1.47), population 3 = 3.12\% (1.47),
population 4 = 2.40\% (0.444). Again, yearly values head a similar mean but
smaller standard deviation.\\

@@

The yearly data assumes the same proportion of each population caught at any
time of the year due to the data aggregation. This assumption introduces
`aggregation bias' as the data may only be representative of some point (or no
point) in time. The monthly data shows some consistency between the real
population and commercial data for population 2 - 4, though population 1 remains
under-represented.  On an annual basis, interestingly the commercial data under
represents the first species (in red) while the survey over represents species
1. This is likely due to the biases in commercial sampling, with the fisheries
not targeting the areas where population 1 are present and the survey sampling
areas where population 1 is more abundant than on average. This indicates that
fixed closures, at the right resolution, when based on commercially derived
data have the potential to reduced fishing mortality. The likely cost of poor
spatial and temporal resolution is associated with reduced effectiveness and
potentially closing fishing opportunities for other fisheries (Figure
\ref{fig:ce}). \\

@@

We consider that the increased availability of high resolution catch and
locational information from commercial fisheries will require it to be a key
source of data for ensuring management is implemented at the right scale in
future. For example, identifying hot-spots for bycatch reduction or identifying
spatial overlaps in mixed fisheries \citep{Dolder2018, Gardner2008, Little2014,
	Dedman2015, Ward2015}. Our simulation model has the potential to test
some of the assumptions behind the modelling approaches in identifying such
hotspots and indeed behind spatiotemporal modelling in general (e.g. comparing
GAMs, GLMMs, Random Forests and geostatistical models under different data
generation processes as exampled by \cite{Stock2019}). \\

@@

\textit{MixFishSim} has numerous potential additional applications as it
enables the user to apply methods to a fisheries system where there is detailed
understanding of underlying spatiotemporal dynamics. This enables
identification of weaknesses or limitations which would not be possible
otherwise. In future, we recommend use of the framework to test hypothesis that
are otherwise unable to be analysed using real world data due to limitations of
data collection. That way the knowledge gained through simulation can inform
the future design of management measures.

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/f_dynamics}
	\caption{Fishing mortality dynamics - the daily fishing mortalities
		across the entire spatial domain showing weekly and seasonal
		patterns in exploitation.  Individual years and the light grey
		lines, the mean of all years the thick black line.}
	\label{fig:10}
\end{figure}

>>>>

\usepackage[draft]{changes}

@@

%% Group authors per affiliation:
\author[1,2]{Paul J. Dolder\corref{c}}
\cortext[c]{Corresponding author}
\ead{paul.dolder@cefas.co.uk}

@@

%%
To understand how data resolution impacts inference on mixed fisheries
interactions we developed a highly resolved spatiotemporal discrete-event
simulation model ('MixFishSim`) incorporating: i) delay-difference population
dynamics, ii) population movement using Gaussian Random Fields to simulate
patchy, heterogeneously distributed populations, and iii) fishery dynamics for
multiple fleet characteristics based on population targeting under an
explore-exploit strategy. This is implemented via a mix of correlated random
walk movement (for exploration) and learned behaviour (for exploitation) phases
of the fisheries. \\ 
%%
Fifty years of sub-daily fishing activity was simulated and used to draw
inference on the underlying community structures. We compared inferences based
on: commercial catch, a simulated fixed-site sampling survey design and the
true \added{(simulated)} underlying populations. We i) establish the potential
limitations of fishery-dependent data in providing a robust picture of
spatiotemporal distributions; and then ii) simulated an area closure based on
areas defined from the different data sources at a range of temporal and
spatial resolutions.\\
%%
Our framework allows users to explore the assumptions in modelling
observational data and evaluate the underlying dynamics of such approaches at a
fine spatial and temporal scale. In application to a mixed fishery exploiting
four different populations we found different spatial patterns were evident and
that the effectiveness of the spatial closure reduced when data were aggregated
across larger spatial areas. However, aggregation across time periods has less
of a negative impact on the closure success and while not as effective as when
based on on the true population, closures based on high catch rates observed in
commercial data could still reduce fishing on a protected species. \\

@@

\begin{enumerate}
	\item Do different source of sampling-derived fisheries data
		reflect\deleted{s} the underlying community structure? 	
	\item How does data aggregation and data source impact on the success
		of spatial fisheries management measures?
\end{enumerate}

@@

Different perceptions of the proportion of each stock in an area are seen when
we aggregate the data over a smaller geographical region at different
timescales, with weekly (top), monthly (middle) and yearly (bottom) catch
compositions from across an aggregated 20 x 20 area (Figure \ref{fig:2}). In
the true population, the monthly aggregation captures the major patterns of
composition seen in the weekly data with the percentage of different
populations in the catch having similar mean and standard deviations.  In the
weekly data population 1 = 9.36\% (SD = 3.99), population 2 = 83.2\% (5.60),
population 3 = 3.57\% (1.23), population 4 = 3.91\% (1.59); in the monthly data
population 1 = 9.23\% (3.87), population 2\% = 83.3 (5.52), population 3 =
3.62\% (1.15), population 4 = \deleted{\%}3.86\added{\%} (1.52). While means
were similar some of the variation was lost when aggregated to an annual level;
population 1 = 9.90\% (0.173), population 2 = 82.2\% (0.308), population 3 =
3.82\% (0.119), population 4 = 4.03\% (0.0502).\\

The commercial data on a weekly basis shows some of the same patterns as the
true population, though the population 1 \deleted{(in red)} is less well
represented and some weeks are missing catches from the area. Here, weekly and
monthly compositions were nearly identical, with monthly composition of
population 1 = 0.0472\% (0.0139), population 2 = 94.4\% (1.47), population 3 =
3.12\% (1.47), population 4 = 2.40\% (0.444). \deleted{Again, y}\added{Y}early
values head a similar mean but smaller standard deviation.\\

@@

The yearly data assumes the same proportion of each population caught at any
time of the year due to the data aggregation. This assumption introduces
`aggregation bias' as the data may only be representative of some point (or no
point) in time. The monthly data shows some consistency between the real
population and commercial data for population 2 - 4, though population 1 remains
under-represented.  On an annual basis, interestingly the commercial data under
represents the first species (in red) while the survey over represents species
1. This is likely due to the biases in commercial sampling, with the fisheries
not targeting the areas where population 1 are present and the survey sampling
areas where population 1 is more abundant than on average. This indicates that
fixed closures, at the right resolution, when based on commercially derived
data have the potential to reduce\deleted{d} fishing mortality. The likely cost
of poor spatial and temporal resolution is associated with reduced
effectiveness and potentially closing fishing opportunities for other fisheries
(Figure \ref{fig:ce}). \\

@@

We consider that the increased availability of high resolution catch and
locational information from commercial fisheries will require it to be a key
source of data for ensuring management is implemented at the right scale in
future. For example, identifying hot-spots for bycatch reduction or identifying
spatial overlaps in mixed fisheries \citep{Dolder2018, Gardner2008, Little2014,
	Dedman2015, Ward2015}. Our simulation model has the potential to test
some of the assumptions behind the modelling approaches in identifying such
hotspots and indeed behind spatiotemporal modelling in general\replaced{,}{ (}e.g. comparing
GAMs, GLMMs, Random Forests and geostatistical models under different data
generation processes as exampled by \cite{Stock2019}deleted{)}. \\

@@

\textit{MixFishSim} has numerous potential additional applications as it
enables the user to apply methods to a fisheries system where there is detailed
understanding of underlying spatiotemporal dynamics. This enables
identification of weaknesses or limitations which would not be possible
otherwise. In future, we recommend use of the framework to test
hypothes\replaced{e}{i}s that are otherwise unable to be analysed using real
world data due to limitations of data collection. That way the knowledge gained
through simulation can inform the future design of management measures.

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/f_dynamics}
	\caption{Fishing mortality dynamics - the daily fishing mortalities
		across the entire spatial domain showing weekly and seasonal
		patterns in exploitation.  Individual years a\replaced{re}{nd}
		the light grey lines, the mean of all years the thick black
		line.}
	\label{fig:10}
\end{figure}
